\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-04-21 paper/main.tex
Added acknowledgements

\setcopyright{none} % to remove the copyright notice
\settopmatter{printacmref=false} % to remove the ACM Reference Format
\renewcommand\footnotetextcopyrightpermission[1]{} % to remove copyright box

@@

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
%% \setcopyright{acmlicensed}
%% \copyrightyear{2018}
%% \acmYear{2018}
%% \acmDOI{XXXXXXX.XXXXXXX}
%% %% These commands are for a PROCEEDINGS abstract or paper.
%% \acmConference[Conference acronym 'XX]{Make sure to enter the correct
%%   conference title from your rights confirmation email}{June 03--05,
%%   2018}{Woodstock, NY}
%% %%
%% %%  Uncomment \acmBooktitle if the title of the proceedings is different
%% %%  from ``Proceedings of ...''!
%% %%
%% %%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%% %%  June 03--05, 2018, Woodstock, NY}
%% \acmISBN{978-1-4503-XXXX-X/2018/06}
%% \acmBooktitle{Companion Proceedings of the 33rd ACM Symposium on the Foundations
%% of Software Engineering (FSE '25), June 23--27, 2025, Trondheim, Norway}
\copyrightyear{2025}
\acmYear{2025}
\setcopyright{acmlicensed}\acmConference[ISSTA Companion '25]{34th ACM SIGSOFT International Symposium on Software Testing and Analysis}{June 25--28, 2025}{Trondheim, Norway}
\acmBooktitle{34th ACM SIGSOFT International Symposium on Software Testing and Analysis (ISSTA Companion '25), June 25--28, 2025, Trondheim, Norway}
\acmDOI{10.1145/3713081.3731739}
\acmISBN{979-8-4007-1474-0/2025/06}
%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

@@

>>>>

% \setcopyright{none} % to remove the copyright notice
% \settopmatter{printacmref=false} % to remove the ACM Reference Format
% \renewcommand\footnotetextcopyrightpermission[1]{} % to remove copyright box

@@

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
%% \setcopyright{acmlicensed}
%% \copyrightyear{2018}
%% \acmYear{2018}
%% \acmDOI{XXXXXXX.XXXXXXX}
%% %% These commands are for a PROCEEDINGS abstract or paper.
%% \acmConference[Conference acronym 'XX]{Make sure to enter the correct
%%   conference title from your rights confirmation email}{June 03--05,
%%   2018}{Woodstock, NY}
%% %%
%% %%  Uncomment \acmBooktitle if the title of the proceedings is different
%% %%  from ``Proceedings of ...''!
%% %%
%% %%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%% %%  June 03--05, 2018, Woodstock, NY}
%% \acmISBN{978-1-4503-XXXX-X/2018/06}
%% \acmBooktitle{Companion Proceedings of the 33rd ACM Symposium on the Foundations
%% of Software Engineering (FSE '25), June 23--27, 2025, Trondheim, Norway}
\setcopyright{acmlicensed}
\copyrightyear{2025}
\acmYear{2025}
\acmDOI{10.1145/3713081.3731739}
\acmConference[ISSTA Companion '25]{34th ACM SIGSOFT International Symposium on Software Testing and Analysis}{June 25--28, 2025}{Trondheim, Norway}
\acmBooktitle{34th ACM SIGSOFT International Symposium on Software Testing and Analysis (ISSTA Companion '25), June 25--28, 2025, Trondheim, Norway}
\acmISBN{979-8-4007-1474-0/2025/06}
%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

@@

\section{Acknowledgements}
This work was supported and funded by the National Science Foundation grant numbers CCF-2349961.
